\bf Longitudinal Principal Manifold Estimation

### 2024-07-26 paper/main.tex

  \caption{{\footnotesize Left Hippocampus and Left Thalamus Cross Sections. LPME-approximated embedding function, shown in blue, routinely falls inside the boundaries of the observed hippocampus surface. In the fifth hippocampus observation with $t=6.55$, the LPME-estimated surface has a gap. Such gaps in the surface estimates frequently correspond with inaccurate volume estimates. The cross sectional plots indicate that the PME and LPME algorithms fit much more closely to the regularly shaped thalamus surface.}}
  \label{fig:adni_cross_sections}
\end{figure}

>>>>

  \caption{{\footnotesize Left Hippocampus and Left Thalamus Cross Sections. LPME-approximated embedding function routinely falls inside the boundaries of the observed hippocampus surface. In the fifth hippocampus observation with $t=2.11$, the LPME-estimated surface has a gap. Such gaps in the surface estimates frequently correspond with inaccurate volume estimates. The cross sectional plots indicate that the PME and LPME algorithms fit much more closely to the regularly shaped thalamus surface.}}
  \label{fig:adni_cross_sections}
\end{figure}
